A better way to format your document for CEUR-WS

### 2024-04-22 paper/paper-part2.tex
refactor literature search for #3

>>>>

Examples further include ``production ready systems'' like NBoost for ElasticSearch.\footnote{\url{https://github.com/koursaros-ai/nboost}}

- NBoost is a scalable, search-api-boosting platform for deploying
transformer models to improve the relevance of search results or
diffe rent platforms (i.e. Elasticsearch) Topics
- maybe more useful for the user pipeline
- is between user and the actual pipeline where it picks the best
based on relevance and training

JMC and DISP~\cite{cui21}:
- Joint Model Compression (JMC)
- Direct Importance-aware Structured Pruning
- Dense Knowledge Distillation (DKD)
- Paper at thulb

MiniLMv2~\cite{wang21} (https://huggingface.co/sentence-transformers/all-MiniLM-L6-v2)
- found in https://arxiv.org/abs/2012.15828 (MiniLMv2)
- they state that their model outperform state of the art models
- uses deep distillated self-attention which are distributed and also
give values to relations to copy teacher self-attention
- transfers knowledge of upper-middle- to last-layer(MiniLM only
mimics the last layer)

Transit(https://arxiv.org/abs/2101.03289)
